\vspace{-1cm} Model simplicity breeds contempt: using simple models to answer basic questions on species' distributions

### 2021-02-10 manuscript/manuscript.tex
Trying with more species because I don't know what else to do

One of the central goals of ecology is to understand the ways species are distributed across space (ref). Over the years, researchers have developed multiple distribution models to try to untangle the factors that play a role in defining such distributions (ref). These models estimate species' realized niches using several covariates, including environmental variables (ref), species ecological traits' (ref) and phylogenetic relations (ref). Moreover, recent work on these modelling approaches has focused on estimating (ref) and accounting for (ref) biotic factors, such as competitive or facilitative relationships. Overall, these methodological advances have provided with crucial ecological insights into the factors shaping species' distributions (ref); however, they have also faced some criticism as a result of the... For example, ...

The use of species distribution models has grown a lot. These models try to estimate species' realized niches using several covariates, including environmental variables (ref), species ecological traits' (ref) and phylogenetic relations (ref). Recent work on these modelling approaches has increasingly focused on estimating (ref) and accounting for (ref) biotic factors, such as competitive or facilitative relationships. The idea is that by understanding how all such factors shape species' distribution we will gain a mechanistic understanding on how these distributions are established and change over time. Unfortunately, while some of this approaches will certainly increase the predictive performance of distribution models (ref), the nature of some of the estimates have been shown to theoretically have some mishaps (ref).

@@

Increasing efforts have been devoted to improving the ability of statistical models to predict the presence/absence of species across ranges (ref). Accurately predicting how species are distributed across ranges, it is crucial for understanding the impacts and effect of global climate change. With that said, accounting for the mechanisms can come at the cost of modelling noise... However, much less attention is paid to how species' distributions compare to each other.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAGRAPH 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A lot can be learned from the basic properties of species' realized niches.

>>>>

One of the central goals of ecology is to understand the ways species are distributed across space (ref). Over the years, researchers have developed multiple distribution models to try to untangle the factors that play a role in defining such distributions (ref). These models estimate species' realized niches using several covariates, including environmental variables (ref), species ecological traits' (ref) and phylogenetic relations (ref). Recent work on these approaches has focused on estimating (ref) and accounting for (ref) biotic factors, such as competitive or facilitative relationships. The idea is that by understanding how such biotic and abiotic factors shape species' distributions, we can gain a mechanistic understanding on how ecological communities are established and change over time. Unfortunately, while some of this approaches can increase the predictive performance of distribution models (ref), the nature of some of the estimates have been theoretically questioned (ref). For example...

%Overall, these methodological advances have provided with crucial ecological insights into the factors shaping species' distributions (ref); however, they have also faced some criticism as a result of the... For example, ...
%
%The use of species distribution models has grown a lot. These models try to estimate species' realized niches using several covariates, including environmental variables (ref), species ecological traits' (ref) and phylogenetic relations (ref). Recent work on these modelling approaches has increasingly focused on estimating (ref) and accounting for (ref) biotic factors, such as competitive or facilitative relationships. The idea is that by understanding how all such factors shape species' distribution we will gain a mechanistic understanding on how these distributions are established and change over time. Unfortunately, while some of this approaches will certainly increase the predictive performance of distribution models (ref), the nature of some of the estimates have been shown to theoretically have some mishaps (ref).

@@

Increasing efforts have been devoted to improving the ability of statistical models to predict the presence/absence of species across ranges (ref). Accurately predicting how species are distributed across ranges is crucial for understanding the impacts and effect of global climate change. With that said, accounting for the mechanisms can come at the cost of modelling noise... However, much less attention is paid to how species' distributions compare to each other.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAGRAPH 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While the value of gaining a mechanistic understanding of species' distributions is unquestioned, a lot can be learned from shedding light on basic properties of species' realized niches.
